LaMachine: A meta-distribution for NLP software

### 2019-01-28 docs/lamachine_clarin2018.tex
[paper] more major edits after feedback by iris; edited case study 2 and added a paragraph on maintainability of LaMachine

@@

LaMachine offered a convenient platform for a range of different explorations and experiments in the area of NLP and text mining.
However, for some situations LaMachine was not a good fit for the tasks at hand: For team members who did not have
experience with a non-Windows environment, LaMachine was not a suitable or useful tool. And also for members who wanted
to use a graphical user interface for their text editors as we did not manage to get the x-forwarding working (note that
this also depends on the overall VM). After a few attempts the team gave up on resolving this issue due to time pressure
but it also demonstrated that fine-tuning the configuration of LaMachine on certain aspects is beyond the reach of a data scientist without system administration skills.
 %iris it moet nog wat beter geformuleerd worden maar je snaprt wat ik bedoel

>>>>

The flexibility LaMachine offers, with various flavours and versions, makes it more accessible and deployable in
multiple contexts, but this does come at a cost. Maintaining LaMachine itself is a non-trivial task that requires
constant maintenance and testing\footnote{We run automated tested on a continuous integration platform to this end};
software exists in an ever moving ecosystem. Any of the distributions we target, or software that participates, \emph{might}
at any time introduce a change that requires us to adapt LaMachine accordingly. Similarly, underlying Linux
distribution releases that are currently up-to-date and supported, will eventually be deprecated and replaced by newer releases, a development
LaMachine is obliged to follow by design.

@@

LaMachine offered a convenient platform for a range of different explorations and experiments in the area of NLP and
text mining.  However, for some situations LaMachine, or rather Linux in general, was not a good fit for the audience of
the workshop: For team members who did not have experience with a non-Windows environment, LaMachine was not a suitable
or useful tool. The limit of LaMachine was also reached for members who wanted to use desktop text editors with a
graphical user interface as this is not offered by LaMachine and we did not manage to get X-forwarding working in the
Ubuntu Linux VM. After a few attempts the team gave up on resolving this issue due to time pressure. This, also
demonstrates that fine-tuning the configuration of LaMachine on certain aspects is beyond the reach of a data scientist
without system administration skills. But this certainly also applies also to the installation as a whole in the
SURFsara context, which involved things like the partitioning, formatting and mounting of (virtual) drives and setting
up user accounts on the shared VM, all of which require some system administration skills.
 %verwerkt <-- <iris> it moet nog wat beter geformuleerd worden maar je snaprt wat ik bedoel
%@iris: hebben jullie verder geen gebruik proberen te maken van de Jupyter Lab omgeving? Dat biedt in ieder geval iets
%grafisch wat via web te benaderen is?
